---
title: "Final Models for Paper"
author: "Mikaela Meyer"
date: "1/22/2021"
output: html_document
---

This document will contain the final models we intend to use for our paper.

```{r setup, include=FALSE}
library(dplyr)
library(readxl)
library(knitr)
library(miceadds)
library(aods3)
library(car)
library(tidyverse)
library(ggplot2)
library(grid)
library(ggDiagnose)
library(gridExtra)
```

```{r, echo = FALSE}
# all crime: 2018-2020
crime_1820 <- read_excel("crime_3yrs.xlsx")
# remove first and last week of the year since they do not
# fall into any month by our categorization
crime_1820_df <- crime_1820[!(crime_1820$Week_Group == "0"),]
crime_1820_df$Year <- as.factor(crime_1820_df$Year)

# Remove weeks greater than week 38 for 2020
crime_1820_df <- crime_1820_df %>% filter(Week <= 38 | Year != "2020")

# Create new response variables
crime_1820_df$Homicide_avg_byPop <- (crime_1820_df$Homicide_avg*52*100000)/crime_1820_df$Population
crime_1820_df$Homicide_diff_byPop <- (100000*crime_1820_df$Homicide*52)/crime_1820_df$Population - crime_1820_df$Homicide_avg_byPop

crime_1820_df$Robbery_avg_byPop <- (crime_1820_df$Robbery_avg*52*100000)/crime_1820_df$Population
crime_1820_df$Robbery_diff_byPop <- (100000*crime_1820_df$Robbery*52)/crime_1820_df$Population - crime_1820_df$Robbery_avg_byPop

crime_1820_df$Burglary_avg_byPop <- (crime_1820_df$`Burglary All_avg`*52*100000)/crime_1820_df$Population
crime_1820_df$Burglary_diff_byPop <- (100000*crime_1820_df$`Burglary All`*52)/crime_1820_df$Population - crime_1820_df$Burglary_avg_byPop

crime_1820_df$Auto_avg_byPop <- (crime_1820_df$`Auto Theft_avg`*52*100000)/crime_1820_df$Population
crime_1820_df$Auto_diff_byPop <- (100000*crime_1820_df$`Auto Theft`*52)/crime_1820_df$Population - crime_1820_df$Auto_avg_byPop

crime_1820_df$Larceny_avg_byPop <- (crime_1820_df$Larceny_avg*52*100000)/crime_1820_df$Population
crime_1820_df$Larceny_diff_byPop <- (100000*crime_1820_df$Larceny*52)/crime_1820_df$Population - crime_1820_df$Larceny_avg_byPop

### aggravated assault results for discussion section

# crime_1820_df$AggAssault_avg_byPop <- (crime_1820_df$`Aggravated Assault_avg`*52*100000)/crime_1820_df$Population
# crime_1820_df$AggAssault_diff_byPop <- (100000*crime_1820_df$`Aggravated Assault`*52)/crime_1820_df$Population - crime_1820_df$AggAssault_avg_byPop

# Filter out cities that aren't in top 70
crime_1820_df <- crime_1820_df %>% 
  filter(!City %in% c("Baton Rouge", "Chattanooga",
                      "Gainesville", "Hartford",
                      "Tacoma", "Tempe"))

# Remove first 11 weeks of 2019 for Kansas City due to the
# data being unavailable
crime_1820_df <- crime_1820_df %>% filter(!(City == "Kansas City" & Week %in% 1:11 & Year == "2019"))

# Clean Closeness index to make openness index
crime_1820_df <- mutate(crime_1820_df, 
                        Openness_Index =
                          abs(Closeness_Index - 14))
```

```{r,echo=FALSE}
# Diagnostic Plots Function
multi_panel_diag <- function(lm.out, plot_choice_vec,save="no",filename="NA"){
  my_df <- dfCompile(lm.out)
  ii <- 1
  if(plot_choice_vec==c("all")){
    plot_choice_vec <- c("qq","std","stud","lev","Cook","CookvLev")
  }
  
  my_list <- vector("list",length(plot_choice_vec))
  
  if("qq" %in% plot_choice_vec){
    qqplot <- ggDiagnose(lm.out,which=2, return = T, show.plot = F)[[2]]$qqnorm
    my_list[[ii]] <- qqplot
    ii <- ii + 1
  }
  if("std" %in% plot_choice_vec){
    stdplot <- ggplot(my_df,aes(x=.yhat, y=.std.resid))+geom_point()+
      geom_hline(yintercept=-2,color="red",linetype="dashed")+
      geom_hline(yintercept=0)+geom_hline(yintercept=2, color="red",
                                          linetype="dashed")+
      labs(title = "Std. Res vs Fit Vals", x = "Fitted Values", 
           y = "Std. Residuals")
    my_list[[ii]] <- stdplot
    ii <- ii+1
  }
  if("stud" %in% plot_choice_vec){
    my_df$.student.resid <- rstudent(lm.out)
    studplot <- ggplot(my_df,aes(x=.yhat,y=.student.resid))+geom_point()+ 
      geom_hline(yintercept=-2,color="red",linetype="dashed")+
      geom_hline(yintercept=0)+geom_hline(yintercept=2,color="red",
                                          linetype="dashed")+
      labs(title = "Stud. Res vs Fit",x="Fitted Values",
           y = "Studentized Residuals")
    my_list[[ii]] <- studplot
    ii <- ii + 1
  }
  if("lev" %in% plot_choice_vec){
    lev <- ggplot(my_df, aes(x=.index,y=.leverage))+geom_point()+
      labs(title="Leverage vs. Index",x="Index",y="Leverage")
    my_list[[ii]] <- lev
    ii <- ii + 1
  }
  if("Cook" %in% plot_choice_vec){
    cook <- ggDiagnose(lm.out,which = 4, return = T, show.plot = F)[[2]]$cooks
    my_list[[ii]] <- cook
    ii <- ii + 1
  }
  if("CookvLev" %in% plot_choice_vec){
    cook_v_lev <- ggDiagnose(lm.out,which=6,
                             return=T,
                             show.plot = F)[[2]]$cooks.vs.logit.leverage+labs(title="Cook's Dist v. Lev")
    my_list[[ii]] <- cook_v_lev
    ii <- ii + 1
  }
  ncol <- ifelse(length(my_list)==1,1,ifelse(length(my_list)==2,
                 2,ifelse(length(my_list)==3,3,ifelse(length(my_list)==4,2,3))))
  grid.arrange(grobs=my_list,ncol=ncol)
  if(save=="yes"){
    save_obj <- arrangeGrob(grobs=my_list,ncol=ncol)
    ggsave(file=paste(filename,".jpg"),save_obj)
  }
}
```

```{r, echo = FALSE}
# Create new variable: 2020 flag to be used in interactions for month model
crime_1820_df$Year_2020 <- ifelse(crime_1820_df$Year == "2020", 1, 0)
crime_1820_df$Month <- as.factor(crime_1820_df$Month) #Otherwise, the first month isn't absorbed

#create data frame for openness index and biweekly lockdown models; stops at week 21
crime_openness <- crime_1820_df %>% filter(Week < min(Week[Surge_Protest_Week == 1]) | Year != "2020") 

#create data frame for openness index; these cities do
#not have openness index data available
crime_openness_idx <- crime_openness %>% filter(!City %in% c("Tulsa", "Mesa",
                                                         "Raleigh", "Milwaukee",
                                                         "Saint Paul"))
```

### Homicide 

#### Seasonal Crime Rate

```{r}
hom_seasonal <- lm.cluster(data = crime_1820_df, formula = `Homicide_diff_byPop` ~ Year + Month + Year_2020*Month, cluster = 'City')

summary(hom_seasonal)
```

##### Results Plot (Fig. 1)

```{r, echo=FALSE}
#' Create data frame of desired results from clustered regression model
#'
#' @param mylm the clustered regression model object
#' @param myavg the 2018 average crime rate
#' @param sigvec a vector of "yes" and "no" that tells whether each main
#' effect coefficient is significant at alpha = 0.05 level
#' @param sig2020vec a vector of "yes" and "no" that tells whether each 
#' 2020 interaction term is significant at alpha = 0.05 level
#'
#' @return res_df, which has columns for the month number, the coefficients of interest,
#' their standard errors, and whether they're significant; each row is a month
#'
#' 

create_res_df <- function(mylm, myavg, sigvec, sig2020vec){
  std_errors <- diag(sqrt(vcov(mylm)))
  res_df <- data.frame("MonthNum" = c(2:12), "Coef" = 
                         coef(mylm)[c(7:14, 4:6)],
                       "CoefSE" = std_errors[c(7:14, 4:6)],
                       "Coef2020" = coef(mylm)[c(19:26, 16:18)],
                       "Coef2020SE" = c(std_errors[15:22], NA, NA, NA),
                       "Value" = myavg + coef(mylm)[c(7:14, 4:6)],
                       "Value2020" = myavg + coef(mylm)[c(7:14, 4:6)] + 
                         coef(mylm)[c(19:26, 16:18)],
                       "Sig0.05" = sigvec,
                       "Sig0.052020" = sig2020vec)
  return(res_df)
}

#' Create data frame that contains all necessary components for monthly 
#' model ggplots
#'
#' @param res_df a data frame created by `create_res_df` function
#'
#' @return a data frame that has duplicate rows for each month;
#' one month contains the plotting info for the main month effect, 
#' while the other contains the plotting info for the 2020 month interaction effect

create_graph_df <- function(res_df){
  graph_df1 <- res_df %>% select(MonthNum, Value, Value2020,
                                          CoefSE, Coef2020SE) %>%
    pivot_longer(cols = c(Value, Value2020), names_to = "Name", 
                 values_to = "CrimeRate")
  graph_df2 <- res_df %>% select(MonthNum, Sig0.05, Sig0.052020,
                                          CoefSE, Coef2020SE) %>%
  pivot_longer(cols = c(Sig0.05, Sig0.052020), names_to = "Significance",
               values_to = "Significant")
  graph_df <- cbind(graph_df1, graph_df2[,-c(1:3)]) #remove duplicate columns
  graph_df <- graph_df %>% mutate(Month = recode_factor(
    MonthNum, `1` = "Jan.",
    `2` = "Feb.",
    `3` = "Mar.",
    `4` = "Apr.",
    `5` = "May",
    `6` = "Jun.",
    `7` = "Jul.",
    `8` = "Aug.",
    `9` = "Sep.",
    `10` = "Oct.",
    `11` = "Nov.",
    `12` = "Dec.")
  )
  graph_df$UpperBd <- ifelse(graph_df$Name == "Value2020",
                               graph_df$CrimeRate + 
                                 (1.96*graph_df$Coef2020SE),
                               NA)
  graph_df$LowerBd <- ifelse(graph_df$Name == "Value2020",
                               graph_df$CrimeRate - 
                                 (1.96*graph_df$Coef2020SE),
                               NA)
  return(graph_df)
}

#' Function to create the monthly model results graph
#'
#' @param graph_df a dataframe produced by `create_graph_df` function
#' @param myavg the average across January of each year; to be plotted as dotted black line
#' @param mymonths a vector of abbreviations for months to appear on the axis
#'
#' @return a ggplot object that is the plot we desire for monthly model results

create_month_res_graph <- function(graph_df, myavg, mymonths){
  res_graph <- ggplot(graph_df, aes(x = MonthNum, y = CrimeRate)) +
    geom_line(aes(color = Name)) +
    geom_errorbar(graph_df, mapping = aes(x = MonthNum,
                                            y = CrimeRate,
                                            ymax = UpperBd, 
                                            ymin = LowerBd),
                color = "dark orange") +
    geom_point(aes(color = Name, shape = Name), size = 2) + 
    geom_hline(yintercept=myavg, linetype = "dotted") +
    scale_shape_manual(values=c(16, 17), na.translate = FALSE,
                       name = "Seasonal Trend", labels =
                           c("Avg.", "2020")) + 
    labs(x = "Month") +
    scale_x_continuous(breaks = seq(2, 12, 2), labels = mymonths) +
    scale_color_manual(values = c("blue", "dark orange"), 
                       name = "Seasonal Trend", labels =
                           c("Avg.", "2020"))
  return(res_graph)
}

#Values that will be necessary for all graphs
mymonths <- c("Feb.", "Apr.", "Jun.", "Aug.", "Oct.", "Dec.")
text_lockdown <- textGrob("Lockdowns\nbegin", gp = gpar(fontsize = 8,
                                                        fontface = "bold",
                                                        col = "red"))
text_protest <- textGrob("Protests\nbegin", gp = gpar(fontsize = 8, 
                                                      fontface = "bold",                                                      col = "red"))
```

```{r,echo=FALSE}
sig_hom = c("No", "No", "No", "Yes", "Yes", "Yes", "Yes", "No", "No", "No", 
            "No")
sig_hom2020 = c("No", "No", "No", "No", "Yes", "No", "No", "No", NA, NA, NA)
hom_jan_mean <- mean(crime_1820_df$Homicide_avg_byPop[
  crime_1820_df$Month == 1])

hom_result_df <- create_res_df(hom_seasonal, 
                                    hom_jan_mean, sig_hom, sig_hom2020)

hom_graph_df <- create_graph_df(hom_result_df)

hom_month_graph <- create_month_res_graph(hom_graph_df, 
                                          hom_jan_mean, mymonths) +
  labs(x = "Month", y = "Homicide Rate per 100K People", 
       title = "Homicide Rate by Month") +
  theme(plot.title = element_text(hjust = 0.5), 
        plot.margin = unit(c(1,1,2,1), "lines")) +
  ylim(0, 45) + annotation_custom(text_lockdown, xmin = 3.75, xmax = 3.75, 
                    ymin = -12, ymax = -12) +
  annotation_custom(text_protest, xmin = 6, xmax = 6,
                    ymin = -12, ymax = -12) + 
  annotation_custom(segmentsGrob(gp = gpar(col = 
                                             "red", lwd = 2)), 
        xmin=3.75, xmax=3.75,ymin=-3, ymax=-1.75) +
  annotation_custom(segmentsGrob(gp = gpar(col = 
                                             "red",
                                           lwd = 2)),
                    xmin = 6, xmax = 6, ymin = -3,
                    ymax = -1.75) +
  coord_cartesian(clip = "off")

hom_month_graph
```

##### Diagnostics

```{r,echo=FALSE}
hom_seasonal_lm <- lm(data = crime_1820_df, formula=`Homicide_diff_byPop`  ~ Year + Month + Year_2020*Month)

multi_panel_diag(hom_seasonal_lm, "all")
```

#### Biweekly Lockdown Model

```{r}
hom_biweek <- lm.cluster(data=crime_openness, Homicide_diff_byPop ~ Year + Month + `LD_-1/0` + `LD_1/2` + `LD_3/4` + `LD_5/6` + `LD_7/8` + `LD_9/10`,
                              cluster = 'City')

summary(hom_biweek)
```

##### Diagnostics

```{r,echo=FALSE}
hom_biweek_lm <- lm(data = crime_openness, formula=Homicide_diff_byPop ~ Year + Month + `LD_-1/0` + `LD_1/2` + `LD_3/4` + `LD_5/6` + `LD_7/8` + `LD_9/10`)

multi_panel_diag(hom_biweek_lm, "all")
```

##### Results Plot (Fig. 2)

```{r,echo=FALSE}
hom_open_std_errors <- diag(sqrt(vcov(hom_biweek)))
hom_open_graph_df <- data.frame("BiweekVar" = c("-1/0", "1/2",
                                                "3/4", "5/6",
                                                "7/8", "9/10"),
                                "Coef" = coef(hom_biweek)[15:20],
                                "Upper" = coef(hom_biweek)[15:20] +
                                  (1.96*hom_open_std_errors[15:20]),
                                "Lower" = coef(hom_biweek)[15:20] -
                                  (1.96*hom_open_std_errors[15:20]))

ggplot(hom_open_graph_df, aes(x = BiweekVar, y = Coef)) +
  geom_point(color = "dark green") + geom_errorbar(aes(ymin = Lower,
                                             ymax = Upper), color = "dark green") +
  labs(x = "Weeks since Lockdown", y = "Lockdown Impact",
       title = "Homicide Biweekly Lockdown Indicator Model Results") +
  geom_hline(yintercept = 0, linetype = "dotted") +
  theme(plot.title = element_text(hjust = 0.5)) + ylim(-15, 15)
```

#### Openness Index Model

```{r}
hom_openness_idx <- lm.cluster(data=crime_openness_idx, Homicide_diff_byPop ~ Year + Month + Openness_Index, cluster = 'City')

summary(hom_openness_idx)
```

##### Diagnostics

```{r,echo=FALSE}
hom_openness_idx_lm <- lm(data = crime_openness_idx, formula=Homicide_diff_byPop ~ Year + Month + Openness_Index)

multi_panel_diag(hom_openness_idx_lm, "all")
```

### Burglary

#### Seasonal Crime Rates

```{r}
burg_seasonal <- lm.cluster(data = crime_1820_df, formula = Burglary_diff_byPop ~ Year + Month +
                                    Year_2020*Month, cluster = 'City')

summary(burg_seasonal)
```

##### Diagnostics 

```{r,echo=FALSE}
burg_seasonal_lm <- lm(data = crime_1820_df, formula=Burglary_diff_byPop ~ Year + Month + Year_2020*Month)

multi_panel_diag(burg_seasonal_lm, "all")
```

##### Results Plot (Fig. 3)

```{r, echo=FALSE}
burg_jan_mean <- mean(crime_1820_df$Burglary_avg_byPop[crime_1820_df$Month == 1])
sig_burg = c("Yes", "Yes", "No", "Yes", "No", "Yes", "Yes", "No", "No", "No", "No")
sig_burg2020 = c("No", "No", "No", "No", "Yes", "No", "No", "No", NA, NA, NA)

burg_result_df <- create_res_df(burg_seasonal, 
                                    burg_jan_mean, sig_burg, sig_burg2020)

burg_graph_df <- create_graph_df(burg_result_df)

burg_month_graph <- create_month_res_graph(burg_graph_df,
                                          burg_jan_mean,
                                          mymonths) + 
  labs(y = "Burglary Rate per 100K People", 
       title = "Burglary Rate by Month") + 
  theme(plot.title = element_text(hjust = 0.5)) + ylim(500, 925) +
  annotation_custom(text_lockdown, xmin = 3.75, xmax = 3.75, 
                    ymin = 435, ymax = 435) +
  annotation_custom(text_protest, xmin = 6, xmax = 6,
                    ymin = 435, ymax = 435) + 
  annotation_custom(segmentsGrob(gp = gpar(col = 
                                             "red", lwd = 2)), 
        xmin=3.75, xmax=3.75,ymin=475, ymax=485) +
  annotation_custom(segmentsGrob(gp = gpar(col = 
                                             "red",
                                           lwd = 2)),
                    xmin = 6, xmax = 6, ymin = 475,
                    ymax = 485) +
  coord_cartesian(clip = "off")

burg_month_graph
```

#### Biweekly Lockdown Model

```{r}
burg_biweek <- lm.cluster(data=crime_openness, Burglary_diff_byPop ~ Year + Month + `LD_-1/0` + `LD_1/2` + `LD_3/4` + `LD_5/6` + `LD_7/8` + `LD_9/10`,
                               cluster = 'City')

summary(burg_biweek)
```

##### Diagnostics

```{r,echo=FALSE}
burg_biweek_lm <- lm(data = crime_openness, formula=Burglary_diff_byPop ~ Year + Month + `LD_-1/0` + `LD_1/2` + `LD_3/4` + `LD_5/6` + `LD_7/8` + `LD_9/10`)

multi_panel_diag(burg_biweek_lm, "all")
```

##### Results Plot (Fig. 4)

```{r,echo = FALSE}
burg_open_std_errors <- diag(sqrt(vcov(burg_biweek)))
burg_open_graph_df <- data.frame("BiweekVar" = c("-1/0", "1/2",
                                                "3/4", "5/6",
                                                "7/8", "9/10"),
                                "Coef" = coef(burg_biweek)[15:20],
                                "Upper" = coef(burg_biweek)[15:20] +
                                  (1.96*burg_open_std_errors[15:20]),
                                "Lower" = coef(burg_biweek)[15:20] -
                                  (1.96*burg_open_std_errors[15:20]))

ggplot(burg_open_graph_df, aes(x = BiweekVar, y = Coef)) +
  geom_point(color = "dark green") + geom_errorbar(aes(ymin = Lower,
                                             ymax = Upper), color = "dark green") +
  labs(x = "Weeks since Lockdown", y = "Lockdown Impact",
       title = "Burglary Biweekly Lockdown Indicator Model Results") +
  geom_hline(yintercept = 0, linetype = "dotted") +
  theme(plot.title = element_text(hjust = 0.5)) + ylim(-200, 1000)
```

#### Openness Index Model

```{r}
burg_openness_idx <- lm.cluster(data=crime_openness_idx, Burglary_diff_byPop ~ Year + Month + Openness_Index, cluster = 'City')

summary(burg_openness_idx)
```

##### Diagnostics

```{r,echo=FALSE}
burg_openness_idx_lm <- lm(data = crime_openness_idx, formula=Burglary_diff_byPop ~ Year + Month + Openness_Index)

multi_panel_diag(burg_openness_idx_lm, "all")
```

### Auto Theft

#### Seasonal Crime Trends

```{r}
auto_seasonal <- lm.cluster(data = crime_1820_df, formula = Auto_diff_byPop ~ Year + Month +
                                    Year_2020*Month, cluster = 'City')

summary(auto_seasonal)
```

##### Diagnostics 

```{r,echo=FALSE}
auto_seasonal_lm <- lm(data = crime_1820_df, formula=Auto_diff_byPop ~ Year + Month + Year_2020*Month)

multi_panel_diag(auto_seasonal_lm, "all")
```

##### Results Plot (Fig. 5)

```{r,echo=FALSE}
auto_jan_mean <- mean(crime_1820_df$Auto_avg_byPop[crime_1820_df$Month == 1])
sig_auto = c("Yes", "Yes", "Yes", "No", "No", "No", "No", "No", "No", "No", "No")
sig_auto2020 = c("No", "No", "No", "No", "Yes", "Yes", "Yes", "Yes", NA, NA, NA)

auto_result_df <- create_res_df(auto_seasonal, 
                                    auto_jan_mean, sig_auto, sig_auto2020)

auto_graph_df <- create_graph_df(auto_result_df)

auto_month_graph <- create_month_res_graph(auto_graph_df,
                                          auto_jan_mean,
                                          mymonths) + 
  labs(y = "Auto Theft Rate per 100K People", 
       title = "Auto Theft Rate by Month") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  ylim(375, 800) +
  annotation_custom(text_lockdown, xmin = 3.75, xmax = 3.75, 
                    ymin = 310, ymax = 310) +
  annotation_custom(text_protest, xmin = 6, xmax = 6,
                    ymin = 310, ymax = 310) + 
  annotation_custom(segmentsGrob(gp = gpar(col = 
                                             "red", lwd = 2)), 
        xmin=3.75, xmax=3.75,ymin=345, ymax=360) +
  annotation_custom(segmentsGrob(gp = gpar(col = 
                                             "red",
                                           lwd = 2)),
                    xmin = 6, xmax = 6, ymin = 345,
                    ymax = 360) +
  coord_cartesian(clip = "off")

auto_month_graph
```

#### Biweekly Lockdown Model

```{r}
auto_biweek <- lm.cluster(data=crime_openness, Auto_diff_byPop ~ Year + Month + `LD_-1/0` + `LD_1/2` + `LD_3/4` + `LD_5/6` + `LD_7/8` + `LD_9/10`, cluster = 'City')

summary(auto_biweek)
```

##### Diagnostics

```{r,echo=FALSE}
auto_biweek_lm <- lm(data = crime_openness, formula=Auto_diff_byPop ~ Year + Month + `LD_-1/0` + `LD_1/2` + `LD_3/4` + `LD_5/6` + `LD_7/8` + `LD_9/10`)

multi_panel_diag(auto_biweek_lm, "all")
```

##### Results Plot (Fig. 6)

```{r,echo = FALSE}
auto_open_std_errors <- diag(sqrt(vcov(auto_biweek)))
auto_open_graph_df <- data.frame("BiweekVar" = c("-1/0", "1/2",
                                                "3/4", "5/6",
                                                "7/8", "9/10"),
                                "Coef" = coef(auto_biweek)[15:20],
                                "Upper" = coef(auto_biweek)[15:20] +
                                  (1.96*auto_open_std_errors[15:20]),
                                "Lower" = coef(auto_biweek)[15:20] -
                                  (1.96*auto_open_std_errors[15:20]))

ggplot(auto_open_graph_df, aes(x = BiweekVar, y = Coef)) +
  geom_point(color = "dark green") + geom_errorbar(aes(ymin = Lower,
                                             ymax = Upper), color = "dark green") +
  labs(x = "Weeks since Lockdown", y = "Lockdown Impact",
       title = "Auto Theft Biweekly Lockdown Indicator Model Results") +
  geom_hline(yintercept = 0, linetype = "dotted") +
  theme(plot.title = element_text(hjust = 0.5)) +
    ylim(-100, 250)
```

#### Openness Index Model

```{r}
auto_openness_idx <- lm.cluster(data=crime_openness_idx, Auto_diff_byPop ~ Year + Month + Openness_Index, cluster = 'City')

summary(auto_openness_idx)
```

##### Diagnostics

```{r,echo=FALSE}
auto_openness_idx_lm <- lm(data = crime_openness_idx, formula=Auto_diff_byPop ~ Year + Month + Openness_Index)

multi_panel_diag(auto_openness_idx_lm, "all")
```

### Robbery

#### Seasonal Crime Rate

```{r}
rob_seasonal <- lm.cluster(data = crime_1820_df, formula = Robbery_diff_byPop ~ Year + Month +
                                    Year_2020*Month, cluster = 'City')

summary(rob_seasonal)
```

##### Diagnostics

```{r,echo=FALSE}
rob_seasonal_lm <- lm(data = crime_1820_df, formula=Robbery_diff_byPop ~ Year + Month + Year_2020*Month)

multi_panel_diag(rob_seasonal_lm, "all")
```

##### Results Plot (Fig. 7)

```{r,echo=FALSE}
rob_jan_mean <- mean(crime_1820_df$Robbery_avg_byPop[crime_1820_df$Month == 1])
sig_rob = c("Yes", "Yes", "Yes", "No", "No", "Yes", "Yes", "Yes", "No", "No", "No")
sig_rob2020 = c("No", "No", "No", "Yes", "No", "Yes", "Yes", "Yes", NA, NA, NA)

rob_result_df <- create_res_df(rob_seasonal, 
                                    rob_jan_mean, sig_rob, sig_rob2020)

rob_graph_df <- create_graph_df(rob_result_df)

rob_month_graph <- create_month_res_graph(rob_graph_df,
                                          rob_jan_mean,
                                          mymonths) + 
  labs(y = "Robbery Rate per 100K People", 
       title = "Robbery Rate by Month") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
  ylim(175, 350) + 
  annotation_custom(text_lockdown, xmin = 3.75, xmax = 3.75, 
                    ymin = 148, ymax = 148) +
  annotation_custom(text_protest, xmin = 6, xmax = 6,
                    ymin = 148, ymax = 148) + 
  annotation_custom(segmentsGrob(gp = gpar(col = 
                                             "red", lwd = 2)), 
        xmin=3.75, xmax=3.75,ymin= 162, ymax=170) +
  annotation_custom(segmentsGrob(gp = gpar(col = 
                                             "red",
                                           lwd = 2)),
                    xmin = 6, xmax = 6, ymin = 162,
                    ymax = 170) +
  coord_cartesian(clip = "off")

rob_month_graph
```

#### Biweekly Lockdown Model

```{r}
rob_biweek <- lm.cluster(data=crime_openness, Robbery_diff_byPop ~ Year + Month + `LD_-1/0` + `LD_1/2` + `LD_3/4` + `LD_5/6` + `LD_7/8` + `LD_9/10`,
                              cluster = 'City')

summary(rob_biweek)
```

##### Diagnostics

```{r,echo=FALSE}
rob_biweek_lm <- lm(data = crime_openness, formula=Robbery_diff_byPop ~ Year + Month + `LD_-1/0` + `LD_1/2` + `LD_3/4` + `LD_5/6` + `LD_7/8` + `LD_9/10`)

multi_panel_diag(rob_biweek_lm, "all")
```

##### Results Plot (Fig. 8)

```{r, echo=FALSE}
rob_open_std_errors <- diag(sqrt(vcov(rob_biweek)))
rob_open_graph_df <- data.frame("BiweekVar" = c("-1/0", "1/2",
                                                "3/4", "5/6",
                                                "7/8", "9/10"),
                                "Coef" = coef(rob_biweek)[15:20],
                                "Upper" = coef(rob_biweek)[15:20] +
                                  (1.96*rob_open_std_errors[15:20]),
                                "Lower" = coef(rob_biweek)[15:20] -
                                  (1.96*rob_open_std_errors[15:20]))

ggplot(rob_open_graph_df, aes(x = BiweekVar, y = Coef)) +
  geom_point(color = "dark green") + geom_errorbar(aes(ymin = Lower,
                                             ymax = Upper), color = "dark green") +
  labs(x = "Weeks since Lockdown", y = "Lockdown Impact",
       title = "Robbery Biweekly Lockdown Indicator Model Results") +
  geom_hline(yintercept = 0, linetype = "dotted") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ylim(-100, 100)
```

#### Openness Index Model

```{r}
rob_openness_idx <- lm.cluster(data=crime_openness_idx, Robbery_diff_byPop ~ Year + Month + Openness_Index, cluster = 'City')

summary(rob_openness_idx)
```

##### Diagnostics

```{r,echo=FALSE}
rob_openness_idx <- lm(data = crime_openness_idx, formula=Robbery_diff_byPop ~ Year + Month + Openness_Index)

multi_panel_diag(rob_openness_idx, "all")
```

### Larceny

#### Seasonal Crime Trends

```{r}
larceny_seasonal <- lm.cluster(data = crime_1820_df, formula = Larceny_diff_byPop ~ Year + Month +
                                    Year_2020*Month, cluster = 'City')

summary(larceny_seasonal)
```

##### Diagnostics

```{r,echo=FALSE}
larceny_seasonal_lm <- lm(data = crime_1820_df, formula=Larceny_diff_byPop ~ Year + Month + Year_2020*Month)

multi_panel_diag(larceny_seasonal_lm, "all")
```

##### Results Plot (Fig. 9)

```{r,echo=FALSE}
larceny_jan_mean <- mean(crime_1820_df$Larceny_avg_byPop[crime_1820_df$Month == 1])
sig_larceny = c("Yes", "Yes", "No", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes")
sig_larceny2020 = c("No", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes", NA, NA, NA)

larceny_result_df <- create_res_df(larceny_seasonal, 
                                    larceny_jan_mean, sig_larceny,
                                   sig_larceny2020)

larceny_graph_df <- create_graph_df(larceny_result_df)

larceny_month_graph <- create_month_res_graph(larceny_graph_df,
                                          larceny_jan_mean,
                                          mymonths) + 
  labs(y = "Larceny Rate per 100K People", 
       title = "Larceny Rate by Month") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  ylim(1500, 3500) +
  annotation_custom(text_lockdown, xmin = 3.75, xmax = 3.75, 
                    ymin = 1200, ymax = 1200) +
  annotation_custom(text_protest, xmin = 6, xmax = 6,
                    ymin = 1200, ymax = 1200) + 
  annotation_custom(segmentsGrob(gp = gpar(col = 
                                             "red", lwd = 2)), 
        xmin=3.75, xmax=3.75,ymin=1350, ymax=1450) +
  annotation_custom(segmentsGrob(gp = gpar(col = 
                                             "red",
                                           lwd = 2)),
                    xmin = 6, xmax = 6, ymin = 1350,
                    ymax = 1450) +
  coord_cartesian(clip = "off")

larceny_month_graph
```

#### Biweekly Lockdown Model

```{r}
larceny_biweek <- lm.cluster(data=crime_openness, Larceny_diff_byPop ~ Year + Month + `LD_-1/0` + `LD_1/2` + `LD_3/4` + `LD_5/6` + `LD_7/8` + `LD_9/10`,
                                  cluster = 'City')

summary(larceny_biweek)
```

##### Diagnostics

```{r,echo=FALSE}
larceny_biweek_lm <- lm(data = crime_openness, formula=Larceny_diff_byPop ~ Year + Month + `LD_-1/0` + `LD_1/2` + `LD_3/4` + `LD_5/6` + `LD_7/8` + `LD_9/10`)

multi_panel_diag(larceny_biweek_lm, "all")
```

##### Results Plot (Fig. 10)

```{r,echo=FALSE}
larceny_open_std_errors <- diag(sqrt(vcov(larceny_biweek)))
larceny_open_graph_df <- data.frame("BiweekVar" = c("-1/0", "1/2",
                                                "3/4", "5/6",
                                                "7/8", "9/10"),
                                "Coef" = coef(larceny_biweek)[15:20],
                                "Upper" = coef(larceny_biweek)[15:20] +
                                  (1.96*larceny_open_std_errors[15:20]),
                                "Lower" = coef(larceny_biweek)[15:20] -
                                  (1.96*larceny_open_std_errors[15:20]))

ggplot(larceny_open_graph_df, aes(x = BiweekVar, y = Coef)) +
  geom_point(color = "dark green") + geom_errorbar(aes(ymin = Lower,
                                             ymax = Upper), color = "dark green") +
  labs(x = "Weeks since Lockdown", y = "Lockdown Impact",
       title = "Larceny Biweekly Lockdown Indicator Model Results") +
  geom_hline(yintercept = 0, linetype = "dotted") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ylim(-1250, 250)
```

#### Openness Index Model

```{r}
larceny_openness_idx <- lm.cluster(data=crime_openness_idx, Larceny_diff_byPop ~ Year + Month + Openness_Index, cluster = 'City')

summary(larceny_openness_idx)
```

##### Diagnostics

```{r,echo=FALSE}
larceny_openness_idx_lm <- lm(data = crime_openness_idx, formula=Larceny_diff_byPop ~ Year + Month + Openness_Index)

multi_panel_diag(larceny_openness_idx_lm, "all")

qqPlot(larceny_openness_idx_lm)
```

### For discussion: Aggravated Assault

```{r}
# agg_seasonal <- lm.cluster(data = crime_1820_df, formula = `AggAssault_diff_byPop` ~ Year + Month + Year_2020*Month, cluster = 'City')
# 
# summary(agg_seasonal)
```

```{r}
# agg_openness_idx <- lm.cluster(data=crime_openness_idx, AggAssault_diff_byPop ~ Year + Month + Openness_Index, cluster = 'City')
# 
# summary(agg_openness_idx)
```

```{r}
# agg_biweek <- lm.cluster(data=crime_openness, AggAssault_diff_byPop ~ Year + Month + `LD_-1/0` + `LD_1/2` + `LD_3/4` + `LD_5/6` + `LD_7/8` + `LD_9/10`,
#                                   cluster = 'City')
# 
# summary(agg_biweek)
```

