---
title: "Models for Statistics and Public Policy"
author: "Mikaela Meyer"
date: "2/15/2022"
output: html_document
---

```{r setup, include=FALSE}
library(dplyr)
library(readxl)
library(knitr)
library(miceadds)
library(aods3)
library(car)
library(tidyverse)
library(ggplot2)
library(grid)
library(magrittr)
#library(ggDiagnose)
library(gridExtra)
library(MASS)
library(modelr)
library(ggrepel)
```

```{r, echo = FALSE}
# all crime: 2018-2020
crime_1820 <- read_excel("crime_3yrs.xlsx")
# remove first and last week of the year since they do not
# fall into any month by our categorization
crime_1820_df <- crime_1820[!(crime_1820$Week_Group == "0"),]
crime_1820_df$Year <- as.factor(crime_1820_df$Year)

# Filter out cities that aren't in top 70
crime_1820_df <- crime_1820_df %>% 
  filter(!City %in% c("Baton Rouge", "Chattanooga",
                      "Gainesville", "Hartford",
                      "Tacoma", "Tempe", "Lincoln")) # Lincoln removed due to lack of late 2020 data

# Remove first 11 weeks of 2019 for Kansas City due to the
# data being unavailable
crime_1820_df <- crime_1820_df %>% filter(!(City == "Kansas City" & Week %in% 1:11 & Year == "2019"))

# Clean Closeness index to make openness index
crime_1820_df <- mutate(crime_1820_df, 
                        Openness_Index =
                          abs(Closeness_Index - 14))
```

```{r, echo = FALSE}
# Create new variable: 2020 flag to be used in interactions for month model
crime_1820_df$Year_2020 <- ifelse(crime_1820_df$Year == "2020", 1, 0)
crime_1820_df$Year_2019 <- ifelse(crime_1820_df$Year == "2019", 1, 0)
crime_1820_df <- crime_1820_df %>% mutate("PrePandemic" = 
                                            ifelse(Year == 2020 & Month %in% c(1, 2), 1, 0),
                                          "Lockdown" = ifelse(Year == 2020 & Month %in% c(3,4,5), 1, 0),
                                          "Protests" = ifelse(Year == 2020 & Month %in% c(6,7,8), 1, 0),
                                          "End" = ifelse(Year ==2020 & Month %in% c(9:12), 1, 0))
crime_1820_df$Month <- as.factor(crime_1820_df$Month) #Otherwise, the first month isn't absorbed

#create data frame for openness index and biweekly lockdown models; stops at week 21
crime_openness <- crime_1820_df %>% filter(Week < min(Week[Surge_Protest_Week == 1]) | Year != "2020") %>%
  filter(City != "Milwaukee")

#create data frame for openness index; these cities do
#not have openness index data available
crime_openness_idx <- crime_openness %>% filter(!City %in% c("Tulsa", "Mesa",
                                                         "Raleigh", "Milwaukee",
                                                         "Saint Paul"))

hom_1820_df <- crime_1820_df %>% filter(City != "San Francisco") 
hom_openness <- crime_1820_df %>% filter(Week < min(Week[Surge_Protest_Week == 1]) | Year != "2020") %>% filter(!City %in% c("Milwaukee", "San Francisco"))

#create data frame for openness index; these cities do
#not have openness index data available
hom_oi <- crime_openness %>% filter(!City %in% c("Tulsa", "Mesa",
                                                         "Raleigh", "Milwaukee",
                                                         "Saint Paul", 
                                                         "San Francisco"))
```

## Homicide 

### Seasonal Crime Rate

```{r,echo=FALSE}
hom_seasonal_pois <- glm.cluster(Homicide ~ Year_2019 + Month + PrePandemic +
                           Lockdown + Protests + End + City +
                           offset(log(Population)), data = hom_1820_df,
                           cluster = "City", family = "poisson")
summary(hom_seasonal_pois)


# can use below code to check dispersion parameter
hsp_no_cluster <- glm(Homicide ~ Year_2019 + Month + PrePandemic +
                           Lockdown + Protests + End +
                           offset(log(Population)), data = hom_1820_df,
                      family = "quasipoisson")
summary(hsp_no_cluster)
```

#### Post Estimation Test

```{r,echo=FALSE}
coef_2020_diff_test <- function(crime_glm, crime_df){
  other_2020_coef <- coef(crime_glm)[15:17]
  prepandemic_coef <- coef(crime_glm)[14]
  coef_diff <- other_2020_coef - prepandemic_coef
  other_2020_var <- diag(vcov(crime_glm))[15:17]
  prepandemic_var <- diag(vcov(crime_glm))[14]
  all_2020_covar <- vcov(crime_glm)[15:17, "PrePandemic"]
  var_diff <- other_2020_var + prepandemic_var - (2*all_2020_covar)

  tstats_new <- coef_diff/sqrt(var_diff)
  pvalues_new <- 2*pt(abs(tstats_new),
                      nrow(crime_df)-length(coef(crime_glm)),
                      lower.tail = F)

  diff_result_df <- data.frame("Effect" = names(coef(crime_glm))[15:17],
                             "DifferenceFromPre" = coef_diff,
                             "Std. Error" = sqrt(var_diff),
                             "t.stat" = tstats_new,
                             "P-value" = pvalues_new)
}

diff_result_df_hom <- coef_2020_diff_test(hom_seasonal_pois, hom_1820_df)
diff_result_df_hom

coef_pair_diff_test <- function(crime_glm, idx1, idx2, crime_df){
  first_coef <- coef(crime_glm)[idx1]
  second_coef <- coef(crime_glm)[idx2]
  coef_diff <- second_coef - first_coef
  first_var <- diag(vcov(crime_glm))[idx1]
  second_var <- diag(vcov(crime_glm))[idx2]
  mycovar <- vcov(crime_glm)[idx1, idx2]
  var_diff <- first_var + second_var - (2*mycovar)
  tstats_new <- coef_diff/sqrt(var_diff)
  pvalues_new <- 2*pt(abs(tstats_new), nrow(crime_df)-length(coef(crime_glm)),
                      lower.tail = F)
  diff_result_df <- data.frame("Effect" = paste0(names(coef(crime_glm))[idx1],
                                                 names(coef(crime_glm))[idx2]),
                             "DifferenceFromPre" = coef_diff,
                             "Std. Error" = sqrt(var_diff),
                             "t.stat" = tstats_new,
                             "P-value" = pvalues_new)
  return(diff_result_df)
}

ldsummer_diff_df_hom <- coef_pair_diff_test(hom_seasonal_pois, 15, 16, hom_1820_df)
ldsummer_diff_df_hom
summerend_diff_df_hom <- coef_pair_diff_test(hom_seasonal_pois, 16, 17, hom_1820_df)
summerend_diff_df_hom
```

### Biweekly

```{r, echo = FALSE}
hom_biweek_pois <- glm.cluster(data = hom_openness, Homicide ~ Year +
                                 Month + `LD_-1/0` + `LD_1/2` + `LD_3/4` +
                                 `LD_5/6` + `LD_7/8` + `LD_9/10` + City +
                                 offset(log(Population)),
                              cluster = 'City', family = "poisson")

summary(hom_biweek_pois)

hbp_no_cluster <- glm(Homicide ~ Year +
                                 Month + `LD_-1/0` + `LD_1/2` + `LD_3/4` +
                                 `LD_5/6` + `LD_7/8` + `LD_9/10` +
                           offset(log(Population)), data = hom_openness,
                      family="quasipoisson")
summary(hbp_no_cluster)
```

### Openness Index 

```{r, echo=FALSE}
hom_openness_pois <- glm.cluster(data=hom_oi, Homicide ~ Year + Month + Openness_Index + City + offset(log(Population)), cluster = 'City', family = "poisson")
summary(hom_openness_pois)

hop_no_cluster <- glm(data=hom_oi, Homicide ~ Year + Month + Openness_Index + offset(log(Population)), family = "quasipoisson")
summary(hop_no_cluster)
```

## Auto Theft

### Seasonal Model

```{r,echo=FALSE}
auto_seasonal_pois <- glm.cluster(data = crime_1820_df, 
                            formula = `Auto Theft` ~ Year_2019 + Month +
                                  PrePandemic + Lockdown + Protests + End + City +
                              offset(log(Population)),
                            cluster = 'City', family = "poisson")
summary(auto_seasonal_pois)

asp_no_cluster <- glm(data = crime_1820_df, 
                            formula = `Auto Theft` ~ Year_2019 + Month +
                                  PrePandemic + Lockdown + Protests + End +
                              offset(log(Population)), 
                      family = "quasipoisson")
summary(asp_no_cluster)
```

#### Post Estimation Test

```{r,echo=FALSE}
diff_result_df_auto <- coef_2020_diff_test(auto_seasonal_pois, crime_1820_df)
diff_result_df_auto

ldsummer_diff_df_auto <- coef_pair_diff_test(auto_seasonal_pois, 15, 16, crime_1820_df)
ldsummer_diff_df_auto
summerend_diff_df_auto <- coef_pair_diff_test(auto_seasonal_pois, 16, 17, crime_1820_df)
summerend_diff_df_auto
```

### Biweekly Model

```{r,echo=FALSE}
auto_biweek_pois <- glm.cluster(data = crime_openness, `Auto Theft` ~ Year +
                                 Month + `LD_-1/0` + `LD_1/2` + `LD_3/4` +
                                 `LD_5/6` + `LD_7/8` + `LD_9/10` + City + 
                                 offset(log(Population)),
                              cluster = 'City', family = "poisson")

summary(auto_biweek_pois)

abp_no_cluster <- glm(data = crime_openness, `Auto Theft` ~ Year +
                                 Month + `LD_-1/0` + `LD_1/2` + `LD_3/4` +
                                 `LD_5/6` + `LD_7/8` + `LD_9/10` +
                                 offset(log(Population)),
                      family = "quasipoisson")
summary(abp_no_cluster)
```

### Openness Index Model

```{r,echo=FALSE}
auto_openness_pois <- glm.cluster(data=crime_openness_idx, `Auto Theft` ~ Year + Month + Openness_Index + City + offset(log(Population)), cluster = 'City',
                                  family = "poisson")
summary(auto_openness_pois)

aop_no_cluster <- glm(data=crime_openness_idx, `Auto Theft` ~ Year + Month + Openness_Index + offset(log(Population)), family = "quasipoisson")
summary(aop_no_cluster)
```

## Burglary

### Seasonal Model

```{r,echo=FALSE}
burg_seasonal_pois <- glm.cluster(data = crime_1820_df, 
                            formula = `Burglary All` ~ Year_2019 + Month +
                                  PrePandemic + Lockdown + Protests + End + City + 
                              offset(log(Population)),
                            cluster = 'City', family = "poisson")
summary(burg_seasonal_pois)
bsp_no_cluster <- glm(data = crime_1820_df, 
                            formula = `Burglary All` ~ Year_2019 + Month +
                                  PrePandemic + Lockdown + Protests + End +
                              offset(log(Population)),
                      family = "quasipoisson")
summary(bsp_no_cluster)
```

#### Post Estimation Test

```{r,echo=FALSE}
diff_result_df_burg <- coef_2020_diff_test(burg_seasonal_pois, crime_1820_df)
diff_result_df_burg

ldsummer_diff_df_burg <- coef_pair_diff_test(burg_seasonal_pois, 15, 16, crime_1820_df)
ldsummer_diff_df_burg
summerend_diff_df_burg <- coef_pair_diff_test(burg_seasonal_pois, 16, 17, crime_1820_df)
summerend_diff_df_burg
```

### Biweekly Model

```{r,echo=FALSE}
burg_biweek_pois <- glm.cluster(data = crime_openness, `Burglary All` ~ Year +
                                 Month + `LD_-1/0` + `LD_1/2` + `LD_3/4` +
                                 `LD_5/6` + `LD_7/8` + `LD_9/10` + City + 
                                 offset(log(Population)),
                              cluster = 'City', family = "poisson")

summary(burg_biweek_pois)

bbp_no_cluster <- glm(data = crime_openness, `Burglary All` ~ Year +
                                 Month + `LD_-1/0` + `LD_1/2` + `LD_3/4` +
                                 `LD_5/6` + `LD_7/8` + `LD_9/10` +
                                 offset(log(Population)),
                      family = "quasipoisson")
summary(bbp_no_cluster)
```

### Openness Index Model

```{r,echo=FALSE}
burg_openness_pois <- glm.cluster(data=crime_openness_idx, `Burglary All` ~ Year + Month + Openness_Index + City +  offset(log(Population)), cluster = 'City',
                                  family = "poisson")
summary(burg_openness_pois)

bop_no_cluster <- glm(data=crime_openness_idx, `Burglary All` ~ Year + Month + Openness_Index + offset(log(Population)), family = "quasipoisson")
summary(bop_no_cluster)
```

## Robbery

### Seasonal Model

```{r,echo=FALSE}
rob_seasonal_pois <- glm.cluster(data = crime_1820_df, 
                            formula = Robbery ~ Year_2019 + Month +
                                  PrePandemic + Lockdown + Protests + End + City + 
                              offset(log(Population)),
                            cluster = 'City', family = "poisson")
summary(rob_seasonal_pois)
rsp_no_cluster <- glm(data = crime_1820_df, 
                            formula = Robbery ~ Year_2019 + Month +
                                  PrePandemic + Lockdown + Protests + End +
                              offset(log(Population)),
                      family = "quasipoisson")
summary(rsp_no_cluster)
```

#### Post Estimation Test

```{r,echo=FALSE}
diff_result_df_rob <- coef_2020_diff_test(rob_seasonal_pois, crime_1820_df)
diff_result_df_rob

ldsummer_diff_df_rob <- coef_pair_diff_test(rob_seasonal_pois, 15, 16, crime_1820_df)
ldsummer_diff_df_rob
summerend_diff_df_rob <- coef_pair_diff_test(rob_seasonal_pois, 16, 17, crime_1820_df)
summerend_diff_df_rob
```

### Biweekly Model

```{r,echo=FALSE}
rob_biweek_pois <- glm.cluster(data = crime_openness, Robbery ~ Year +
                                 Month + `LD_-1/0` + `LD_1/2` + `LD_3/4` +
                                 `LD_5/6` + `LD_7/8` + `LD_9/10` + City + 
                                 offset(log(Population)),
                              cluster = 'City', family = "poisson")

summary(rob_biweek_pois)

rbp_no_cluster <- glm(data = crime_openness, Robbery ~ Year +
                                 Month + `LD_-1/0` + `LD_1/2` + `LD_3/4` +
                                 `LD_5/6` + `LD_7/8` + `LD_9/10` +
                                 offset(log(Population)),
                      family = "quasipoisson")
summary(rbp_no_cluster)
```

### Openness Index Model

```{r,echo=FALSE}
rob_openness_pois <- glm.cluster(data=crime_openness_idx, Robbery ~ Year + Month + Openness_Index + City + offset(log(Population)), cluster = 'City',
                                 family = "poisson")
summary(rob_openness_pois)

rop_no_cluster <- glm(data=crime_openness_idx, Robbery ~ Year + Month + Openness_Index + offset(log(Population)), family = "quasipoisson")
summary(rop_no_cluster)
```

### Openness Index Plot

```{r,echo=FALSE}
rob_oi_plot <- crime_openness_idx %>% filter(Year == 2020) %>% group_by(Week) %>% summarize(AvgOI = mean(Openness_Index)) %>% filter(Week >= 10)
rob_oi_plot <- rob_oi_plot %>% mutate(OIEffect = exp(coef(rob_openness_pois)[15]*AvgOI))
rob_oi_plot <- rob_oi_plot %>% mutate(AxisName = paste0(Week,
                                                        "\n(",
                                                        round(AvgOI, digits = 3), ")"))
rob_oi_plt <- ggplot(rob_oi_plot, aes(x = Week, y = OIEffect)) + geom_point(color = "purple") + geom_line(color = "purple") +
  labs(x = "Week and Average Openness Index Value", y = "Mult. Increase from Openness Index") + scale_x_continuous(breaks = 10:21, labels = rob_oi_plot$AxisName) + theme(axis.text.x = element_text(angle = 90))
rob_oi_plt
```

## Larceny

### Seasonal Model

```{r,echo=FALSE}
larceny_seasonal_pois <- glm.cluster(data = crime_1820_df, 
                            formula = Larceny ~ Year_2019 + Month +
                                  PrePandemic + Lockdown + Protests + End + City + 
                              offset(log(Population)),
                            cluster = 'City', family = "poisson")
summary(larceny_seasonal_pois)

lsp_no_cluster <- glm(data = crime_1820_df, 
                            formula = Larceny ~ Year_2019 + Month +
                                  PrePandemic + Lockdown + Protests + End +
                              offset(log(Population)), family = "quasipoisson")
summary(lsp_no_cluster)
```

#### Post Estimation Test

```{r,echo=FALSE}
diff_result_df_larceny <- coef_2020_diff_test(larceny_seasonal_pois, crime_1820_df)
diff_result_df_larceny

ldsummer_diff_df_larceny <- coef_pair_diff_test(larceny_seasonal_pois, 15, 16, crime_1820_df)
ldsummer_diff_df_larceny
summerend_diff_df_larceny <- coef_pair_diff_test(larceny_seasonal_pois, 16, 17, crime_1820_df)
summerend_diff_df_larceny
```

### Biweekly Model

```{r,echo=FALSE}
larceny_biweek_pois <- glm.cluster(data = crime_openness, Larceny ~ Year +
                                 Month + `LD_-1/0` + `LD_1/2` + `LD_3/4` +
                                 `LD_5/6` + `LD_7/8` + `LD_9/10` + City + 
                                 offset(log(Population)),
                              cluster = 'City', family = "poisson")

summary(larceny_biweek_pois)

lbp_no_cluster <- glm(data = crime_openness, Larceny ~ Year +
                                 Month + `LD_-1/0` + `LD_1/2` + `LD_3/4` +
                                 `LD_5/6` + `LD_7/8` + `LD_9/10` +
                                 offset(log(Population)),
                      family = "quasipoisson")
summary(lbp_no_cluster)
```

### Openness Index Model

```{r,echo=FALSE}
larceny_openness_pois <- glm.cluster(data=crime_openness_idx, Larceny ~ Year + Month + Openness_Index + City + offset(log(Population)), cluster = 'City',
                                     family = "poisson")
summary(larceny_openness_pois)

lop_no_cluster <- glm(data=crime_openness_idx, Larceny ~ Year + Month + Openness_Index + offset(log(Population)), family = "quasipoisson")
summary(lop_no_cluster)
```
