---
title: "Final Models for Paper"
author: "Mikaela Meyer"
date: "5/18/2021"
output: html_document
---

This document will contain the final models we intend to use for our paper.

```{r setup, include=FALSE}
library(dplyr)
library(readxl)
library(knitr)
library(miceadds)
library(aods3)
library(car)
library(tidyverse)
library(ggplot2)
library(grid)
library(ggDiagnose)
library(gridExtra)
```

```{r, echo = FALSE}
# all crime: 2018-2020
crime_1820 <- read_excel("C:/Users/meyer/Downloads/crime_3yrs.xlsx")
# remove first and last week of the year since they do not
# fall into any month by our categorization
crime_1820_df <- crime_1820[!(crime_1820$Week_Group == "0"),]
crime_1820_df$Year <- as.factor(crime_1820_df$Year)

# Remove weeks greater than week 38 for 2020
# crime_1820_df <- crime_1820_df %>% filter(Week <= 38 | Year != "2020")

# Create new response variables
crime_1820_df$Homicide_avg_byPop <- (crime_1820_df$Homicide_avg*52*100000)/crime_1820_df$Population
crime_1820_df$Homicide_diff_byPop <- (100000*crime_1820_df$Homicide*52)/crime_1820_df$Population - crime_1820_df$Homicide_avg_byPop

crime_1820_df$Robbery_avg_byPop <- (crime_1820_df$Robbery_avg*52*100000)/crime_1820_df$Population
crime_1820_df$Robbery_diff_byPop <- (100000*crime_1820_df$Robbery*52)/crime_1820_df$Population - crime_1820_df$Robbery_avg_byPop

crime_1820_df$Burglary_avg_byPop <- (crime_1820_df$`Burglary All_avg`*52*100000)/crime_1820_df$Population
crime_1820_df$Burglary_diff_byPop <- (100000*crime_1820_df$`Burglary All`*52)/crime_1820_df$Population - crime_1820_df$Burglary_avg_byPop

crime_1820_df$Auto_avg_byPop <- (crime_1820_df$`Auto Theft_avg`*52*100000)/crime_1820_df$Population
crime_1820_df$Auto_diff_byPop <- (100000*crime_1820_df$`Auto Theft`*52)/crime_1820_df$Population - crime_1820_df$Auto_avg_byPop

crime_1820_df$Larceny_avg_byPop <- (crime_1820_df$Larceny_avg*52*100000)/crime_1820_df$Population
crime_1820_df$Larceny_diff_byPop <- (100000*crime_1820_df$Larceny*52)/crime_1820_df$Population - crime_1820_df$Larceny_avg_byPop

# Filter out cities that aren't in top 70
crime_1820_df <- crime_1820_df %>% 
  filter(!City %in% c("Baton Rouge", "Chattanooga",
                      "Gainesville", "Hartford",
                      "Tacoma", "Tempe", "Lincoln")) # Lincoln removed due to lack of late 2020 data

# Remove first 11 weeks of 2019 for Kansas City due to the
# data being unavailable
crime_1820_df <- crime_1820_df %>% filter(!(City == "Kansas City" & Week %in% 1:11 & Year == "2019"))

# Clean Closeness index to make openness index
crime_1820_df <- mutate(crime_1820_df, 
                        Openness_Index =
                          abs(Closeness_Index - 14))
```

```{r,echo=FALSE}
# Diagnostic Plots Function
multi_panel_diag <- function(lm.out, plot_choice_vec,save="no",filename="NA"){
  my_df <- dfCompile(lm.out)
  ii <- 1
  if(plot_choice_vec==c("all")){
    plot_choice_vec <- c("qq","std","stud","lev","Cook","CookvLev")
  }
  
  my_list <- vector("list",length(plot_choice_vec))
  
  if("qq" %in% plot_choice_vec){
    qqplot <- ggDiagnose(lm.out,which=2, return = T, show.plot = F)[[2]]$qqnorm
    my_list[[ii]] <- qqplot
    ii <- ii + 1
  }
  if("std" %in% plot_choice_vec){
    stdplot <- ggplot(my_df,aes(x=.yhat, y=.std.resid))+geom_point()+
      geom_hline(yintercept=-2,color="red",linetype="dashed")+
      geom_hline(yintercept=0)+geom_hline(yintercept=2, color="red",
                                          linetype="dashed")+
      labs(title = "Std. Res vs Fit Vals", x = "Fitted Values", 
           y = "Std. Residuals")
    my_list[[ii]] <- stdplot
    ii <- ii+1
  }
  if("stud" %in% plot_choice_vec){
    my_df$.student.resid <- rstudent(lm.out)
    studplot <- ggplot(my_df,aes(x=.yhat,y=.student.resid))+geom_point()+ 
      geom_hline(yintercept=-2,color="red",linetype="dashed")+
      geom_hline(yintercept=0)+geom_hline(yintercept=2,color="red",
                                          linetype="dashed")+
      labs(title = "Stud. Res vs Fit",x="Fitted Values",
           y = "Studentized Residuals")
    my_list[[ii]] <- studplot
    ii <- ii + 1
  }
  if("lev" %in% plot_choice_vec){
    lev <- ggplot(my_df, aes(x=.index,y=.leverage))+geom_point()+
      labs(title="Leverage vs. Index",x="Index",y="Leverage")
    my_list[[ii]] <- lev
    ii <- ii + 1
  }
  if("Cook" %in% plot_choice_vec){
    cook <- ggDiagnose(lm.out,which = 4, return = T, show.plot = F)[[2]]$cooks
    my_list[[ii]] <- cook
    ii <- ii + 1
  }
  if("CookvLev" %in% plot_choice_vec){
    cook_v_lev <- ggDiagnose(lm.out,which=6,
                             return=T,
                             show.plot = F)[[2]]$cooks.vs.logit.leverage+labs(title="Cook's Dist v. Lev")
    my_list[[ii]] <- cook_v_lev
    ii <- ii + 1
  }
  ncol <- ifelse(length(my_list)==1,1,ifelse(length(my_list)==2,
                 2,ifelse(length(my_list)==3,3,ifelse(length(my_list)==4,2,3))))
  grid.arrange(grobs=my_list,ncol=ncol)
  if(save=="yes"){
    save_obj <- arrangeGrob(grobs=my_list,ncol=ncol)
    ggsave(file=paste(filename,".jpg"),save_obj)
  }
}
```

```{r, echo = FALSE}
# Create new variable: 2020 flag to be used in interactions for month model
crime_1820_df$Year_2020 <- ifelse(crime_1820_df$Year == "2020", 1, 0)
crime_1820_df$Year_2019 <- ifelse(crime_1820_df$Year == "2019", 1, 0)
crime_1820_df <- crime_1820_df %>% mutate("PrePandemic" = 
                                            ifelse(Year == 2020 & Month %in% c(1, 2), 1, 0),
                                          "Lockdown" = ifelse(Year == 2020 & Month %in% c(3,4,5), 1, 0),
                                          "Protests" = ifelse(Year == 2020 & Month %in% c(6,7,8), 1, 0),
                                          "End" = ifelse(Year ==2020 & Month %in% c(9:12), 1, 0))
crime_1820_df$Month <- as.factor(crime_1820_df$Month) #Otherwise, the first month isn't absorbed

#create data frame for openness index and biweekly lockdown models; stops at week 21
crime_openness <- crime_1820_df %>% filter(Week < min(Week[Surge_Protest_Week == 1]) | Year != "2020") 

#create data frame for openness index; these cities do
#not have openness index data available
crime_openness_idx <- crime_openness %>% filter(!City %in% c("Tulsa", "Mesa",
                                                         "Raleigh", "Milwaukee",
                                                         "Saint Paul"))
```

### Homicide 

#### Seasonal Crime Rate

```{r}
hom_1820_df <- crime_1820_df %>% filter(City != "San Francisco") 
# need to remove San Francisco because we have no data available for it
hom_seasonal <- lm.cluster(data = hom_1820_df, formula = `Homicide_diff_byPop`~ Year_2019 + Month + PrePandemic + Lockdown + Protests + End, cluster = 'City')

summary(hom_seasonal)
```

##### Post-Estimation Test

```{r}
### Year 2020 + Month Interactions
new_month_coef <- coef(hom_seasonal)["Year_2020"] + 
  coef(hom_seasonal)[15:25]
var_2020 <- vcov(hom_seasonal)["Year_2020", "Year_2020"]
var_effects <- diag(vcov(hom_seasonal))[15:25]
cov_effects_2020 <- vcov(hom_seasonal)[15:25, "Year_2020"]
new_var_effects <- var_2020 + var_effects + (2*cov_effects_2020)

tstats <- new_month_coef/sqrt(new_var_effects)
pvalues <- 2*pt(abs(tstats), nrow(hom_1820_df)-length(coef(hom_seasonal)) - 1, lower.tail = F)

### 2020 coefficients vs prepandemic
coef_2020_diff_test <- function(crime_lm, crime_df){
  other_2020_coef <- coef(crime_lm)[15:17]
  prepandemic_coef <- coef(crime_lm)[14]
  coef_diff <- other_2020_coef - prepandemic_coef
  other_2020_var <- diag(vcov(crime_lm))[15:17]
  prepandemic_var <- diag(vcov(crime_lm))[14]
  all_2020_covar <- vcov(crime_lm)[15:17, "PrePandemic"]
  var_diff <- other_2020_var + prepandemic_var - (2*all_2020_covar)

  tstats_new <- coef_diff/sqrt(var_diff)
  pvalues_new <- 2*pt(abs(tstats_new), 
                      nrow(crime_df)-length(coef(crime_lm)) - 1, 
                      lower.tail = F)

  diff_result_df <- data.frame("Effect" = names(coef(crime_lm))[15:17],
                             "DifferenceFromPre" = coef_diff,
                             "Std. Error" = sqrt(var_diff), 
                             "t.stat" = tstats_new,
                             "P-value" = pvalues_new)
}

diff_result_df_hom <- coef_2020_diff_test(hom_seasonal, hom_1820_df)
diff_result_df_hom
```

##### More Post-Estimation Tests

```{r,echo=FALSE}
# Lockdown vs. protest
lockdown_coef <- coef(hom_seasonal)[15]
protest_coef <- coef(hom_seasonal)[16]
coef_diff_ldp <- protest_coef - lockdown_coef
lockdown_var <- diag(vcov(hom_seasonal))[15]
protest_var <- diag(vcov(hom_seasonal))[16]
covar_ldp <- vcov(hom_seasonal)[15, 16]
var_diff_ldp <- lockdown_var + protest_var - (2*covar_ldp)
tstat_ldp <- coef_diff_ldp/sqrt(var_diff_ldp)
pvalue_ldp <- 2*pt(abs(tstat_ldp), 
                      nrow(hom_1820_df)-length(coef(hom_seasonal)) - 1, 
                      lower.tail = F)

# Lockdown vs. end
end_coef <- coef(hom_seasonal)[17]
coef_diff_lde <- end_coef - lockdown_coef
end_var <- diag(vcov(hom_seasonal))[17]
covar_lde <- vcov(hom_seasonal)[15, 17]
var_diff_lde <- lockdown_var + end_var - (2*covar_lde)
tstat_lde <- coef_diff_lde/sqrt(var_diff_lde)
pvalue_lde <- 2*pt(abs(tstat_lde), 
                      nrow(hom_1820_df)-length(coef(hom_seasonal)) - 1, 
                      lower.tail = F)

diff_result_df_ld <- data.frame("Effect" = names(coef(hom_seasonal))[16:17],
                             "DifferenceFromLockdown" = c(coef_diff_ldp,
                                                          coef_diff_lde),
                             "Std. Error" = sqrt(c(var_diff_ldp, 
                                                   var_diff_lde)), 
                             "t.stat" = c(tstat_ldp, tstat_lde),
                             "P-value" = c(pvalue_ldp, pvalue_lde))

diff_result_df_ld
```

#### Rates tables and averages

```{r, echo=FALSE}
avg_1819_df <- crime_1820_df %>% filter(Year != 2020) %>% 
  mutate(Larceny_avg = (Larceny*100000*52)/Population,
         Burglary_avg = (`Burglary All`*100000*52)/Population,
         Robbery_avg = (Robbery*100000*52)/Population,
         Homicide_avg = (Homicide*100000*52)/Population,
         Auto_avg = (`Auto Theft`*100000*52)/Population)

mean(avg_1819_df$Larceny_avg)
mean(avg_1819_df$Burglary_avg)
mean(avg_1819_df$Robbery_avg)
mean(avg_1819_df$Homicide_avg)
mean(avg_1819_df$Auto_avg)
```

#### Figure 1

```{r,echo=FALSE}
new_seasonal_plt <- function(mylm){
  coef_2020 <- coef(mylm)[14:17]
  std_errors <- diag(sqrt(vcov(mylm)))[14:17]

  graph_df <- data.frame("Partsof2020" = names(coef_2020),
                       "Coefficients" = coef_2020,
                       "UpperBd" = coef_2020 + (1.96*std_errors),
                       "LowerBd" = coef_2020 - (1.96*std_errors))

  graph_df <- graph_df %>% mutate(Partsof2020 = fct_relevel(Partsof2020,
                                                          "PrePandemic",
                                                          "Lockdown",
                                                          "Protests",
                                                          "End"))

  new_plt <- ggplot(graph_df, aes(x = Partsof2020, y = Coefficients)) +
  geom_point(color = "blue") + geom_errorbar(mapping = aes(ymax = UpperBd,
                                                           ymin = LowerBd),
                                             color = "blue") +
  geom_hline(yintercept = 0, linetype = "dotted") 
  return(new_plt)
}

fig1_new <- new_seasonal_plt(hom_seasonal) + 
  labs(x = "Periods of 2020", y = "Change in Homicide Rates") +
  ylim(-10, 25) + scale_x_discrete(labels = c(
    "PrePandemic" = "Pre-Pandemic", "Protests" = "Summer Protests",
    "End" = "End of the Year"))

fig1_new
ggsave("hom_new_fig1.png", fig1_new)
```

#### Appendix Plot (Fig. 12): Seasonal Trends

```{r,echo=FALSE}
jan_18_hom_df <- hom_1820_df %>% select(Year, Month, Homicide, Population) %>%
   mutate(Homicide_per_cap = (Homicide*100000*52)/Population) %>%
   filter(Year == 2018 & Month == "1")
jan_18_avg_hom <- mean(jan_18_hom_df$Homicide_per_cap)
std_errors <- diag(sqrt(vcov(hom_seasonal)))
month_res_df <- data.frame("MonthNum" = c(2:12), "Coef" = 
                         coef(hom_seasonal)[c(6:13, 3:5)],
                       "CoefSE" = std_errors[c(6:13, 3:5)])
month_res_df <- month_res_df %>% mutate(
  "Value2020" = c(coef(hom_seasonal)["PrePandemic"], 
                  rep(coef(hom_seasonal)["Lockdown"], 3),
                  rep(coef(hom_seasonal)["Protests"], 3),
                  rep(coef(hom_seasonal)["End"], 4)),
  "SE2020" = c(std_errors[14], 
               rep(std_errors[15], 3),
               rep(std_errors[16], 3),
               rep(std_errors[17], 4)),
  "MonthCoef2020" = Value2020 + Coef,
  "HomRate" = Coef + jan_18_avg_hom,
  "HomRate2020" = MonthCoef2020 + jan_18_avg_hom,
  "UpperBd" = HomRate2020 + (1.96*SE2020),
  "LowerBd" = HomRate2020 - (1.96*SE2020))

mymonths <- c("Feb.", "Apr.", "Jun.", "Aug.", "Oct.", "Dec.")

hom_seasonal_graph <- ggplot(month_res_df, aes(x = MonthNum)) +
    geom_line(aes(y = HomRate),  color = "dark orange") +
    geom_line(aes(y= HomRate2020), color = "blue") + 
    geom_errorbar(mapping = aes(x = MonthNum,
                                y = HomRate2020,
                                ymax = UpperBd, 
                                ymin = LowerBd),
                color = "blue") +
    geom_point(aes(y = HomRate), color = "dark orange", shape = 16, size = 2) +
    geom_point(aes(y = HomRate2020), color = "blue", shape = 17, size = 2) +
    geom_hline(yintercept=jan_18_avg_hom, linetype = "dotted") +
    labs(x = "Month", y = "Homicide Rate") +
    scale_x_continuous(breaks = seq(2, 12, 2), labels = mymonths) +
  ylim(5, 45)
  

hom_seasonal_graph

ggsave("hom_month_new.png", hom_seasonal_graph)
```

##### Diagnostics

```{r,echo=FALSE}
hom_seasonal_lm <- lm(data = crime_1820_df, formula=`Homicide_diff_byPop`  ~ Year_2019 + Month + PrePandemic + Lockdown + Protests + End)

multi_panel_diag(hom_seasonal_lm, "all")
```

#### Biweekly Lockdown Model

```{r}
hom_biweek <- lm.cluster(data=crime_openness, Homicide_diff_byPop ~ Year + Month + `LD_-1/0` + `LD_1/2` + `LD_3/4` + `LD_5/6` + `LD_7/8` + `LD_9/10`,
                              cluster = 'City')

summary(hom_biweek)
```

##### Diagnostics

```{r,echo=FALSE}
hom_biweek_lm <- lm(data = crime_openness, formula=Homicide_diff_byPop ~ Year + Month + `LD_-1/0` + `LD_1/2` + `LD_3/4` + `LD_5/6` + `LD_7/8` + `LD_9/10`)

multi_panel_diag(hom_biweek_lm, "all")
```

##### Results Plot (Fig. 2)

```{r,echo=FALSE}
hom_open_std_errors <- diag(sqrt(vcov(hom_biweek)))
hom_open_graph_df <- data.frame("BiweekVar" = c("-1/0", "1/2",
                                                "3/4", "5/6",
                                                "7/8", "9/10"),
                                "Coef" = coef(hom_biweek)[15:20],
                                "Upper" = coef(hom_biweek)[15:20] +
                                  (1.96*hom_open_std_errors[15:20]),
                                "Lower" = coef(hom_biweek)[15:20] -
                                  (1.96*hom_open_std_errors[15:20]))

ggplot(hom_open_graph_df, aes(x = BiweekVar, y = Coef)) +
  geom_point(color = "dark green") + geom_errorbar(aes(ymin = Lower,
                                             ymax = Upper), color = "dark green") +
  labs(x = "Weeks since Lockdown", y = "Lockdown Impact") +
  geom_hline(yintercept = 0, linetype = "dotted") +
  ylim(-15, 15)
```

#### Openness Index Model

```{r}
hom_openness_idx <- lm.cluster(data=crime_openness_idx, Homicide_diff_byPop ~ Year + Month + Openness_Index, cluster = 'City')

summary(hom_openness_idx)
```

##### Diagnostics

```{r,echo=FALSE}
hom_openness_idx_lm <- lm(data = crime_openness_idx, formula=Homicide_diff_byPop ~ Year + Month + Openness_Index)

multi_panel_diag(hom_openness_idx_lm, "all")
```

### Auto Theft

#### Seasonal Crime Trends

```{r}
auto_seasonal <- lm.cluster(data = crime_1820_df, formula = Auto_diff_byPop ~ Year_2019 + Month +
                                  PrePandemic + Lockdown + Protests + End, cluster = 'City')

summary(auto_seasonal)
```

### Post-Estimation Test
```{r,echo=FALSE}
diff_result_df_auto <- coef_2020_diff_test(auto_seasonal, 
                                           crime_1820_df)
diff_result_df_auto
```

##### Diagnostics 

```{r,echo=FALSE}
auto_seasonal_lm <- lm(data = crime_1820_df, formula=Auto_diff_byPop ~ Year_2019 + Month +
                                  PrePandemic + Lockdown + Protests + End)

multi_panel_diag(auto_seasonal_lm, "all")
```

##### Results Plot (Fig. 3)

```{r,echo=FALSE}
fig3_new <- new_seasonal_plt(auto_seasonal) + 
  labs(x = "Periods of 2020", y = "Change in Auto Theft Rates") +
  ylim(-150, 250) + scale_x_discrete(labels = c(
    "PrePandemic" = "Pre-Pandemic", "Protests" = "Summer Protests",
    "End" = "End of the Year"))

fig3_new
ggsave("auto_new_fig3.png", fig3_new)
```

#### Biweekly Lockdown Model

```{r}
auto_biweek <- lm.cluster(data=crime_openness, Auto_diff_byPop ~ Year + Month + `LD_-1/0` + `LD_1/2` + `LD_3/4` + `LD_5/6` + `LD_7/8` + `LD_9/10`, cluster = 'City')

summary(auto_biweek)
```

##### Diagnostics

```{r,echo=FALSE}
auto_biweek_lm <- lm(data = crime_openness, formula=Auto_diff_byPop ~ Year + Month + `LD_-1/0` + `LD_1/2` + `LD_3/4` + `LD_5/6` + `LD_7/8` + `LD_9/10`)

multi_panel_diag(auto_biweek_lm, "all")
```


##### Results Plot (Fig. 4)

```{r,echo = FALSE}
auto_open_std_errors <- diag(sqrt(vcov(auto_biweek)))
auto_open_graph_df <- data.frame("BiweekVar" = c("-1/0", "1/2",
                                                "3/4", "5/6",
                                                "7/8", "9/10"),
                                "Coef" = coef(auto_biweek)[15:20],
                                "Upper" = coef(auto_biweek)[15:20] +
                                  (1.96*auto_open_std_errors[15:20]),
                                "Lower" = coef(auto_biweek)[15:20] -
                                  (1.96*auto_open_std_errors[15:20]))

ggplot(auto_open_graph_df, aes(x = BiweekVar, y = Coef)) +
  geom_point(color = "dark green") + geom_errorbar(aes(ymin = Lower,
                                             ymax = Upper), color = "dark green") +
  labs(x = "Weeks since Lockdown", y = "Lockdown Impact") +
  geom_hline(yintercept = 0, linetype = "dotted") +
  ylim(-100, 250)
```

#### Openness Index Model

```{r}
auto_openness_idx <- lm.cluster(data=crime_openness_idx, Auto_diff_byPop ~ Year + Month + Openness_Index, cluster = 'City')

summary(auto_openness_idx)
```

##### Diagnostics

```{r,echo=FALSE}
auto_openness_idx_lm <- lm(data = crime_openness_idx, formula=Auto_diff_byPop ~ Year + Month + Openness_Index)

multi_panel_diag(auto_openness_idx_lm, "all")
```

### Burglary

#### Seasonal Crime Rates

```{r}
burg_seasonal <- lm.cluster(data = crime_1820_df, formula = Burglary_diff_byPop ~ Year_2019 + Month + PrePandemic + Lockdown + Protests + End,
                                cluster = 'City')

summary(burg_seasonal)
```

### Post-Estimation Test

```{r,echo=FALSE}
### 2020 coefficients vs prepandemic
diff_result_df_burg <- coef_2020_diff_test(burg_seasonal, crime_1820_df)
diff_result_df_burg
```

##### Diagnostics 

```{r,echo=FALSE}
burg_seasonal_lm <- lm(data = crime_1820_df, formula=Burglary_diff_byPop ~ Year + Month + Year_2020*Month)

multi_panel_diag(burg_seasonal_lm, "all")
```

##### Results Plot (Fig. 5)

```{r,echo=FALSE}
fig5_new <- new_seasonal_plt(burg_seasonal) + 
  labs(x = "Periods of 2020", y = "Change in Burglary Rates") +
  ylim(-250, 100) + scale_x_discrete(labels = c(
    "PrePandemic" = "Pre-Pandemic", "Protests" = "Summer Protests",
    "End" = "End of the Year"))

fig5_new
ggsave("burg_new_fig5.png", fig5_new)
```

#### Biweekly Lockdown Model

```{r}
burg_biweek <- lm.cluster(data=crime_openness, Burglary_diff_byPop ~ Year + Month + `LD_-1/0` + `LD_1/2` + `LD_3/4` + `LD_5/6` + `LD_7/8` + `LD_9/10`,
                               cluster = 'City')

summary(burg_biweek)
```

##### Diagnostics

```{r,echo=FALSE}
burg_biweek_lm <- lm(data = crime_openness, formula=Burglary_diff_byPop ~ Year + Month + `LD_-1/0` + `LD_1/2` + `LD_3/4` + `LD_5/6` + `LD_7/8` + `LD_9/10`)

multi_panel_diag(burg_biweek_lm, "all")
```

##### Results Plot (Fig. 4)

```{r,echo = FALSE}
burg_open_std_errors <- diag(sqrt(vcov(burg_biweek)))
burg_open_graph_df <- data.frame("BiweekVar" = c("-1/0", "1/2",
                                                "3/4", "5/6",
                                                "7/8", "9/10"),
                                "Coef" = coef(burg_biweek)[15:20],
                                "Upper" = coef(burg_biweek)[15:20] +
                                  (1.96*burg_open_std_errors[15:20]),
                                "Lower" = coef(burg_biweek)[15:20] -
                                  (1.96*burg_open_std_errors[15:20]))

ggplot(burg_open_graph_df, aes(x = BiweekVar, y = Coef)) +
  geom_point(color = "dark green") + geom_errorbar(aes(ymin = Lower,
                                             ymax = Upper), color = "dark green") +
  labs(x = "Weeks since Lockdown", y = "Lockdown Impact") +
  geom_hline(yintercept = 0, linetype = "dotted") +
  ylim(-200, 1000)
```

#### Openness Index Model

```{r}
burg_openness_idx <- lm.cluster(data=crime_openness_idx, Burglary_diff_byPop ~ Year + Month + Openness_Index, cluster = 'City')

summary(burg_openness_idx)
```

##### Diagnostics

```{r,echo=FALSE}
burg_openness_idx_lm <- lm(data = crime_openness_idx, formula=Burglary_diff_byPop ~ Year + Month + Openness_Index)

multi_panel_diag(burg_openness_idx_lm, "all")
```

### Robbery

#### Seasonal Crime Rate

```{r}
rob_seasonal <- lm.cluster(data = crime_1820_df, formula = Robbery_diff_byPop ~ Year_2019 + Month + 
                                 PrePandemic + Lockdown + Protests + End, cluster = 'City')

summary(rob_seasonal)
```

### Post-Estimation Test

```{r,echo=FALSE}
diff_result_df_rob <- coef_2020_diff_test(rob_seasonal, crime_1820_df)
diff_result_df_rob
```

##### Diagnostics

```{r,echo=FALSE}
rob_seasonal_lm <- lm(data = crime_1820_df, formula=Robbery_diff_byPop ~ Year + Month + Year_2020*Month)

multi_panel_diag(rob_seasonal_lm, "all")
```

##### Results Plot (Fig. 7)

```{r,echo=FALSE}
fig7_new <- new_seasonal_plt(rob_seasonal) +
  labs(x = "Periods of 2020", y = "Change in Robbery Rates") +
  ylim(-125, 50) + scale_x_discrete(labels = c(
    "PrePandemic" = "Pre-Pandemic", "Protests" = "Summer Protests",
    "End" = "End of the Year"))

fig7_new
ggsave("rob_fig7_new.png", fig7_new)
```

#### Biweekly Lockdown Model

```{r}
rob_biweek <- lm.cluster(data=crime_openness, Robbery_diff_byPop ~ Year + Month + `LD_-1/0` + `LD_1/2` + `LD_3/4` + `LD_5/6` + `LD_7/8` + `LD_9/10`,
                              cluster = 'City')

summary(rob_biweek)
```

##### Diagnostics

```{r,echo=FALSE}
rob_biweek_lm <- lm(data = crime_openness, formula=Robbery_diff_byPop ~ Year + Month + `LD_-1/0` + `LD_1/2` + `LD_3/4` + `LD_5/6` + `LD_7/8` + `LD_9/10`)

multi_panel_diag(rob_biweek_lm, "all")
```

##### Results Plot (Fig. 8)

```{r, echo=FALSE}
rob_open_std_errors <- diag(sqrt(vcov(rob_biweek)))
rob_open_graph_df <- data.frame("BiweekVar" = c("-1/0", "1/2",
                                                "3/4", "5/6",
                                                "7/8", "9/10"),
                                "Coef" = coef(rob_biweek)[15:20],
                                "Upper" = coef(rob_biweek)[15:20] +
                                  (1.96*rob_open_std_errors[15:20]),
                                "Lower" = coef(rob_biweek)[15:20] -
                                  (1.96*rob_open_std_errors[15:20]))

ggplot(rob_open_graph_df, aes(x = BiweekVar, y = Coef)) +
  geom_point(color = "dark green") + geom_errorbar(aes(ymin = Lower,
                                             ymax = Upper), color = "dark green") +
  labs(x = "Weeks since Lockdown", y = "Lockdown Impact") +
  geom_hline(yintercept = 0, linetype = "dotted") +
  ylim(-100, 100)
```

#### Openness Index Model

```{r}
rob_openness_idx <- lm.cluster(data=crime_openness_idx, Robbery_diff_byPop ~ Year + Month + Openness_Index, cluster = 'City')

summary(rob_openness_idx)
```

##### Diagnostics

```{r,echo=FALSE}
rob_openness_idx <- lm(data = crime_openness_idx, formula=Robbery_diff_byPop ~ Year + Month + Openness_Index)

multi_panel_diag(rob_openness_idx, "all")
```

### Larceny

#### Seasonal Crime Trends

```{r}
larceny_seasonal <- lm.cluster(data = crime_1820_df, formula = Larceny_diff_byPop ~ Year_2019 + Month +
                                     PrePandemic + Lockdown + Protests + End, cluster = 'City')

summary(larceny_seasonal)
```

### Post-Estimation Test

```{r,echo=FALSE}
diff_result_df_larceny <- coef_2020_diff_test(larceny_seasonal, crime_1820_df)
diff_result_df_larceny
```

##### Diagnostics

```{r,echo=FALSE}
larceny_seasonal_lm <- lm(data = crime_1820_df, formula=Larceny_diff_byPop ~ Year + Month + Year_2020*Month)

multi_panel_diag(larceny_seasonal_lm, "all")
```

##### Results Plot (Fig. 9)

```{r,echo=FALSE}
fig9_new <- new_seasonal_plt(larceny_seasonal) +
  labs(x = "Periods of 2020", y = "Change in Larceny Rates") +
  ylim(-1250, 750) + scale_x_discrete(labels = c(
    "PrePandemic" = "Pre-Pandemic", "Protests" = "Summer Protests",
    "End" = "End of the Year"))

fig9_new
ggsave("larceny_fig9_new.png", fig9_new)
```

#### Biweekly Lockdown Model

```{r}
larceny_biweek <- lm.cluster(data=crime_openness, Larceny_diff_byPop ~ Year + Month + `LD_-1/0` + `LD_1/2` + `LD_3/4` + `LD_5/6` + `LD_7/8` + `LD_9/10`,
                                  cluster = 'City')

summary(larceny_biweek)
```

##### Diagnostics

```{r,echo=FALSE}
larceny_biweek_lm <- lm(data = crime_openness, formula=Larceny_diff_byPop ~ Year + Month + `LD_-1/0` + `LD_1/2` + `LD_3/4` + `LD_5/6` + `LD_7/8` + `LD_9/10`)

multi_panel_diag(larceny_biweek_lm, "all")
```

##### Results Plot (Fig. 10)

```{r,echo=FALSE}
larceny_open_std_errors <- diag(sqrt(vcov(larceny_biweek)))
larceny_open_graph_df <- data.frame("BiweekVar" = c("-1/0", "1/2",
                                                "3/4", "5/6",
                                                "7/8", "9/10"),
                                "Coef" = coef(larceny_biweek)[15:20],
                                "Upper" = coef(larceny_biweek)[15:20] +
                                  (1.96*larceny_open_std_errors[15:20]),
                                "Lower" = coef(larceny_biweek)[15:20] -
                                  (1.96*larceny_open_std_errors[15:20]))

ggplot(larceny_open_graph_df, aes(x = BiweekVar, y = Coef)) +
  geom_point(color = "dark green") + geom_errorbar(aes(ymin = Lower,
                                             ymax = Upper), color = "dark green") +
  labs(x = "Weeks since Lockdown", y = "Lockdown Impact") +
  geom_hline(yintercept = 0, linetype = "dotted") +
  ylim(-1250, 250)
```

#### Openness Index Model

```{r}
larceny_openness_idx <- lm.cluster(data=crime_openness_idx, Larceny_diff_byPop ~ Year + Month + Openness_Index, cluster = 'City')

summary(larceny_openness_idx)
```

##### Diagnostics

```{r,echo=FALSE}
larceny_openness_idx_lm <- lm(data = crime_openness_idx, formula=Larceny_diff_byPop ~ Year + Month + Openness_Index)

multi_panel_diag(larceny_openness_idx_lm, "all")

qqPlot(larceny_openness_idx_lm)
```